### 2014-10-21 paper/include/dtail.tex
reordering of sections

For DTail-R, the Retention Time data $n$ consists of three bits and is interpreted in such way that the refresh period can become \(64ms \times 2^n, n = [0..7]\). With DTail-V, one additional bit is added to the refresh data which is used to indicate if the row is valid or not. With this structure of four bits per row, the amount of memory required is $0.006\%$ of DRAM capacity assuming a row size of $8\:KB$.

When a row is to be scheduled for refresh the refresh data is checked. If the row is valid and the time since the last refresh is \(64ms \times 2^n, n = [0..7]\) a refresh is performed, otherwise not. The refreshes can be done either by ROR or by CBR depending on what is most efficient at the time. If a large number of rows need refresh then CBR is selected, otherwise ROR is used.

>>>>

For DTail-R, the Retention Time data $n$ consists of three bits and is interpreted in such way that the refresh period can become \(64\:ms \times 2^n, n = [0..7]\). With DTail-V, one additional bit is added to the refresh data which is used to indicate if the row is valid or not. With this structure of four bits per row, the amount of memory required is $0.006\%$ of DRAM capacity assuming a row size of \textit{8 KB}.

When a row is to be scheduled for refresh the refresh data is checked. If the row is valid and the time since the last refresh is \(64\:ms \times 2^n, n = [0..7]\) a refresh is performed, otherwise not. The refreshes can be done either by ROR or by CBR depending on what is most efficient at the time. If a large number of rows need refresh then CBR is selected, otherwise ROR is used.
